### 2013-09-24 nyu/paper.tex
caption below tables

\begin{table*}[t]
    \caption{Quantitative comparison of the proposed method with the
    literature.\tablabel{results}}
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}l@{}cccccc}
\toprule
                        & \footnotesize{ground}        &  \footnotesize{structure}    & \footnotesize{furniture}     & \footnotesize{props}         & \footnotesize{class avg.}   & \footnotesize{pixel avg.}\\
\cmidrule{1-7}

@@

\bottomrule
\end{tabularx}
\quad\\The best value in each column is printed in bold$^\dagger$. The upper part of
the table shows contributions by different parts of our pipeline. RF stands for random forest prediction, RF + SP for aggregated
random forests prediction within superpixels, RF + SP + SVM for an SVM trained on the unary potentials, and RF + SP + CRF is
our proposed pipeline. We optimized our approach for class average
accuracy.\\
$^\dagger$ \footnotesize Note that the work of \citet{stueckler2013} is not directly
comparable, as they integrated information over multiple frames, and did not
measure accuracy for pixels without valid depth measurement.
\end{table*}

>>>>

\begin{table*}[t]
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}l@{}cccccc}
\toprule
                        & \footnotesize{ground}        &  \footnotesize{structure}    & \footnotesize{furniture}     & \footnotesize{props}         & \footnotesize{class avg.}   & \footnotesize{pixel avg.}\\
\cmidrule{1-7}

@@

\bottomrule
\end{tabularx}
    \caption{Quantitative comparison of the proposed method with the
        literature.
The best value in each column is printed in bold$^\dagger$. The upper part of
the table shows contributions by different parts of our pipeline. RF stands for random forest prediction, RF + SP for aggregated
random forests prediction within superpixels, RF + SP + SVM for an SVM trained on the unary potentials, and RF + SP + CRF is
our proposed pipeline. We optimized our approach for class average\tablabel{results}
accuracy.\\
$^\dagger$ \footnotesize Note that the work of \citet{stueckler2013} is not directly
comparable, as they integrated information over multiple frames, and did not
measure accuracy for pixels without valid depth measurement.}
\end{table*}

### 2013-09-24 structured_prediction/paper.tex
caption below tables

\section{CRFs for Semantic Segmentation}
Structured models based on factor graphs, as described in \Secref{factor_graphs} are often
referred to as Conditional Random Fields (CRFs), pointing to their
probabilistic interpretation.
Conditional Random Fields have been established as an important tool in many
areas of computer vision. Applications include dense stereo, optical flow, 
inpainting, de-noising, image editing, low-level segmentation and semantic segmentation.

>>>>

\section{CRFs for Semantic Segmentation}\seclabel{semantic_segmentation}
Structured models based on factor graphs, as described in \Secref{factor_graphs} are often
referred to as Conditional Random Fields (CRFs), pointing to their
probabilistic interpretation.
Conditional Random Fields have been established as an important tool in many
areas of computer vision. Applications include dense stereo, optical flow, 
inpainting, de-noising, image editing, low-level segmentation and semantic segmentation.
